\texttt{davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2022-11-23 paper/main.tex
minor typo fixes to 2.2.3

\begin{itemize}
\item \texttt{.active}: This attribute controls whether support for \texttt{smuggle}
  statements and onion comments) is enabled (\texttt{True}) or
  disabled (\texttt{False}).  When \texttt{davos} is first imported),
  the \texttt{.active} attribute is set to \texttt{True}.

@@

\bibliographystyle{elsarticle-num}
\bibliography{CDL-bibliography/cdl}

>>>>

\begin{itemize}
\item \texttt{.active}: This attribute controls whether support for \texttt{smuggle}
  statements and onion comments is enabled (\texttt{True}) or
  disabled (\texttt{False}).  When \texttt{davos} is first imported,
  the \texttt{.active} attribute is set to \texttt{True}.

@@

\bibliographystyle{elsarticle-num}
\bibliography{main}
